sims

### 2024-12-15 sims/sims.Rmd
update figures sims

```{r}
haz_plot <- function(df_pid, df_group) {
  ggplot(df_group, aes(x = bin, y = group_outcomen, 
                   colour = condition, fill=condition)) +
  geom_line(linewidth=1) + 
  geom_point(size=3) +
  geom_jitter(data=df_pid, aes(y=outcomen), height=0, width = 0.1, alpha = 0.5) +
  geom_errorbar(aes(ymin = group_outcomen-sem, ymax = group_outcomen+sem),
                width=.2, linewidth=1) +
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x="timebin",
       y="probability")
}
```

@@

ggsave("sims/figures/rt_haz.jpeg",
       width = 12, height = 8, dpi=800)
```

@@

ggsave("sims/figures/haz_surv.jpeg",
       width = 7, height = 5, dpi=800)
```

@@

```{r}
p11.1 <-ggplot(minimallt, aes(x = period, y = probability,
                         colour = dv)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=probability-se, ymax=probability+se), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  ggtitle("hazard and survivor functions") +
  xlab("timebin")
p11.1

@@

```{r}
p12.1 <-ggplot(lifetable2, aes(x = period, y = hazard,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  ggtitle("hazard")  +
  xlab("timebin") + ylab("probability") + guides(color=guide_legend(title="prime type"))
p12.1
```

@@

```{r}
p12.2 <-ggplot(ca, aes(x = period, y = ca,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("timebin") +
  ylab("probability") +
  ggtitle("conditional accuracy") + 
  guides(color=guide_legend(title="prime type"))
p12.2
```

>>>>

```{r}
haz_plot <- function(df_pid, df_group) {
  ggplot(df_group, aes(x = bin, y = group_outcomen, 
                   colour = condition, fill=condition)) +
  geom_line(linewidth=1) + 
  geom_point(size=3) +
  geom_jitter(data=df_pid, aes(y=outcomen), height=0, width = 0.1, alpha = 0.5) +
  geom_errorbar(aes(ymin = group_outcomen-sem, ymax = group_outcomen+sem),
                width=.2, linewidth=1) +
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x="time bin",
       y="probability")
}
```

@@

#ggsave("sims/figures/rt_haz.jpeg",
#      width = 12, height = 8, dpi=800)
```

@@

#ggsave("sims/figures/haz_surv.jpeg",
#       width = 7, height = 5, dpi=800)
```

@@

```{r}
p11.1 <-ggplot(minimallt, aes(x = period, y = probability,
                         colour = dv)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=probability-se, ymax=probability+se), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  ggtitle("hazard and survivor functions") +
  xlab("time bin")
p11.1

@@

```{r}
p12.1 <-ggplot(lifetable2, aes(x = period, y = hazard,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  ggtitle("hazard")  +
  xlab("time bin") + ylab("probability") + guides(color=guide_legend(title="prime type"))
p12.1
```

@@

```{r}
p12.2 <-ggplot(ca, aes(x = period, y = ca,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("time bin") +
  ylab("probability") +
  ggtitle("conditional accuracy") + 
  guides(color=guide_legend(title="prime type"))
p12.2
```
